HW 1

### 2022-09-13 HW1/HW1.Rmd
update HW1

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

@@

# 3

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

library(tidyverse)
library(gridExtra)
```

@@

# 3
I used the logistic growth equation to model electric vehicle shares. The equation is given as
\[f(t) = \frac{e^{a+bt}}{1+e^{a+bt}}\]
where $f(t)$ is the fraction of electric vehicles, $t$ is the year, and $a$ and $b$ are coefficients.

Data from 2011\textendash 2019 were obtained from [https://afdc.energy.gov/data/] and [https://www.epa.gov/automotive-trends/explore-automotive-trends-data#SummaryData]. The adfc data include total EV sales by year, and the epa data include information on all car production. I am only considering fully-electric vehicles as EVs for this analysis (not plug-in hybrid EVs).

```{r}
cars <- read_csv("HW1/data/table_export.csv") %>% 
	mutate(`Model Year` = as.integer(`Model Year`),
				 `Production (000)` = as.integer(`Production (000)`)) %>% 
	filter(`Regulatory Class` == "Car",
				 `Vehicle Type` == "All Car",
				 Manufacturer == "All",
				 `Model Year` %in% 2011:2019) %>% 
	mutate(`Model Year` = as.character(`Model Year`))

evs <- read_csv("HW1/data/10567_pev_sales_2-28-20.csv") %>% 
	filter(Type == "EV") %>% 
	select(-Vehicle, -Type) %>% 
	colSums() %>% 
	{tibble(Year = names(.),
					EVs = .)} 
```

Plotting the sale of EVs and total vehicles gives:

```{r}
ev_plot <- evs %>% 
	ggplot(aes(x = Year, y = EVs/1000)) +
	geom_point() +
	ylab("EV Sales (x1000)")

cars_plot <- cars  %>% 
	ggplot(aes(x = `Model Year`, y = `Production (000)`)) +
	geom_point() +
	ylim(c(0, NA)) +
	labs(x = "Year",
			 y = "Car Sales (x1000)")

grid.arrange(ev_plot, cars_plot, ncol = 1)
```

And the share of EVs:

```{r}
evshare <- cars %>% 
	transmute(Year = `Model Year`,
						Cars = `Production (000)` * 1000) %>% 
	left_join(evs, by = "Year") %>% 
	mutate(ev_share = EVs / Cars)

evshare %>% 
	ggplot(aes(x = Year, y = ev_share)) +
	geom_point() +
	ylab("Share of EVs Sold vs. All Cars")
```

Finding a logistic growth model:

```{r}
data <- tibble(year = as.numeric(evshare$Year),
							 share = as.numeric(evshare$ev_share))

formula <- share~(exp(a+b*year)/(1+exp(a+b*year)))
formula <- share~(exp(a)/(1+exp(a)))
formula <- share~SSlogis(year, 1, median(year), 1)
# model <- 
	nls(formula,
			# start = list(a = 1, b = 0.1),
			data = data,
			trace = TRUE)
```
